### 2024-01-14 inst/scripts/papertest.Rmd

```{r runburnin,warning=FALSE,message=FALSE,results='hold',cache=TRUE}
tstep=500
tpcomu=initcomus
tpcomu$occupation[,]=1
burnin=modelVector(
   K=ki, m=1, b=0.2, r=0, rho=0, d=0.04, maturity=18, endrepro=65, 
   population=population, 
   comus=tpcomu, 
   tstep=tstep, 
   tp=generatePathways(z = z) , #we recreate a temporary neutral trait table with no neutral transmission
   age.threshold=20, 
   out=c("finalpop","finalcomus"),   #we only want the final population
   beta=-1,
   logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 100
)
population=resetIds(burnin$population)
initcomus$size=burnin$finalcomus$size
```

>>>>

```{r runburnin,warning=FALSE,message=FALSE,results='hold',cache=TRUE}
tstep=500
tpcomu=initcomus
tpcomu$occupation[,]=1
burnin=modelVector(
   K=ki, m=1, b=0.2, r=0, rho=0, d=0.04, maturity=18, endrepro=65, 
   population=population, 
   comus=tpcomu, 
   tstep=tstep, 
   tp=generatePathways(z = z) , #we recreate a temporary neutral trait table with no neutral transmission
   age.threshold=20, 
   out=c("finalpop","finalcomus"),   #we only want the final population
   beta=-1,
   logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 100
)
population=resetIds(burnin$population)
initcomus$size=burnin$finalcomus$size
traitsid=paste0("t",1:z)
```

### 2024-01-14 inst/scripts/testDemo.Rmd

neutraltraitsParam=generatePathways(z = 2)
traitsid=paste0("t",1:2)
percomu=50
K=2
km=0
ki=2
N=100
pos=random2Dgrid(K=K,Gx=5)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=2,km=0,traits=a,coordinates=pos,G=5,plot=T,sizes=c(50,50))
communities=unlist(lapply(1:K,function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(N,age="random",community = communities),generateTraitsMatrix(N,z))
initcomus$size=unname(table(smallpop[,"community"]))
multrep=replicate(10,modelVector(K=K, m=1, b=0.39, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=smallpop, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","deaths","popsize","popfull","repros","births"),logging=c("time","fission"),ma=1,traitsid=paste0("t",1:z),F_Th=180))

plot(quickV$popsize)
plot(quickV$births)
plot(quickV$deaths)
plot(quickV$repros/quickV$popsize[-1],type="l")

@@

bs=round(runif(100,.35,.41),digit=2)
library(parallel)
cl<-makeCluster(10,type="FORK",outfile="log.txt")
allpopsiz=parSapply(cl,bs,function(b){
           res=modelVector(K=K, m=1, b=b, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=smallpop, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("popsize"),logging=c("done"),ma=1,traitsid=paste0("t",1:z),F_Th=180)
           res$popsize[length(res$popsize)]
})
stopCluster(cl)

>>>>

neutraltraitsParam=generatePathways(z = 2)
traitsid=paste0("t",1:2)
percomu=50
K=2
km=0
ki=2
N=100
pos=random2Dgrid(K=K,Gx=5)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=2,km=0,traits=a,coordinates=pos,G=5,plot=T,sizes=c(50,50))

communities=unlist(lapply(1:K,function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(N,age="random",community = communities),generateTraitsMatrix(N,z))
initcomus$size=unname(table(smallpop[,"community"]))
multrep=replicate(10,modelVector(K=K, m=1, b=0.39, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=smallpop, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","deaths","popsize","popfull","repros","births"),logging=c("time","fission"),ma=1,traitsid=paste0("t",1:z),F_Th=180))

plot(quickV$popsize)
plot(quickV$births)
plot(quickV$deaths)
plot(quickV$repros/quickV$popsize[-1],type="l")
initcomus$occupation[,]=1
communities=unlist(lapply(1:K,function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(K*50,age="random",community = communities),initNeutralTraits(K*50,2))
newtestres=modelVector(K=K, m=1, b=0.5, r=0, rho=.5, d=0.03, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("repros","births","deaths","popsize","finalpop"),logging=c("time"),ma=1,traitsid=paste0("t",1:2),F_Th = 55)

table(newtestres$population[,"community"])
population=newtestres$population

rmid=population[population[,"fid"]==-1,"id"]
population=population[population[,"fid"]!=-1,]
population=population[!(population[,"partner"]%in% rmid),]
initcomus$size=unname(table(population[,"community"]))

@@

bs=round(runif(100,.35,.41),digit=2)
devtools::load_all(".")
bs=round(runif(500,.34,.38),digit=3)
data(smallpop)
traitsid=paste0("t",1:4)
K=10
km=0
ki=10
pos=random2Dgrid(K=K,Gx=100)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=2,km=0,traits=a,coordinates=pos,G=100,plot=T,sizes=50)
initcomus$size=unname(table(smallpop[,"community"]))
library(parallel)
cl<-makeCluster(10,type="FORK",outfile="log.txt")
allpopsiz=parSapply(cl,bs,function(b){
           res=modelVector(K=K, m=1, b=b, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=smallpop, comus=initcomus, tstep=500, tp=initNeutralTraitsPathways(z=4),age.threshold=20, out=c("popsize"),logging=c("done"),ma=1,traitsid=traitsid,F_Th=100)$popsize
})
stopCluster(cl)
par(mfrow=c(1,3))
boxplot(lengths(allpopsiz)~bs,ylab="simu length vs birth rate ",xlab="birth rate",main="extinctions")
finished=allpopsiz[lengths(allpopsiz)==500]
finsize=sapply(finished,"[",500)
boxplot(finsize~bs[lengths(allpopsiz)==500],ylab="population size at the end of simulation for simulation who finised",xlab="birth rate ",main="pop at end without extinctions")
abline(h=nrow(smallpop),col="red")
boxplot(finsize~bs[lengths(allpopsiz)==500],ylab="population size at the end of simulation for simulation who finised",xlab="birth rate ",ylim=c(1,1500),log="y",main="pop at end without extinctions")

allfinal=sapply(allpopsiz,function(i)i[length(i)])
boxplot(allfinal~bs,ylab="population size at the end of simulation for simulation who finised",xlab="birth rate ",main="pop at end ")
abline(h=nrow(smallpop),col="red")

boxplot(log(allfinal+1))

neutraltraitsParam=generatePathways(z = 2)
traitsid=paste0("t",1:2)
percomu=50
K=10
km=0
ki=10
pos=random2Dgrid(K=K,Gx=100)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=ki,km=km,traits=a,coordinates=pos,G=100,plot=T,sizes=c(50))
initcomus$occupation[,]=1
communities=unlist(lapply(1:K,function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(K*50,age="random",community = communities),(K*50,2))
newtestres=modelVector(K=K, m=1, b=0.8, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("repros","births","deaths","popsize","finalpop"),logging=c("time"),ma=1,traitsid=paste0("t",1:2),F_Th = 70)
table(newtestres$population[,"community"])
population=newtestres$population
rmid=population[population[,"fid"]==-1,"id"]
population=population[population[,"fid"]!=-1,]
population=population[!(population[,"partner"]%in% rmid),]
initcomus$size=unname(table(population[,"community"]))
population=resetIds(population)

traitsid=paste0("t",1:2)
K=10
km=0
ki=10
pos=random2Dgrid(K=K,Gx=100)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=2,km=0,traits=a,coordinates=pos,G=100,plot=T)
initcomus$size=unname(table(population[,"community"]))
library(parallel)
bs=round(runif(200,.3,.44),digit=3)
cl<-makeCluster(10,type="FORK",outfile="log.txt")
allpopsizesonly=parSapply(cl,bs,function(b){
           modelVector(K=K, m=1, b=b, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=1000, tp=generatePathways(z=2),age.threshold=20, out=c("popsize"),logging=c("done"),ma=1,traitsid=traitsid,F_Th=100,testdebug=F)$popsize
})
stopCluster(cl)
saveRDS(file="pposizeLargerTh.RDS",allpopsizesonly)
par(mfrow=c(1,3))
boxplot(lengths(allpopsiz)~bs,ylab="simu length vs birth rate ",xlab="birth rate",main="extinctions")
finished=allpopsiz[lengths(allpopsiz)==500]
finsize=sapply(finished,"[",500)
boxplot(finsize~bs[lengths(allpopsiz)==500],ylab="population size at the end of simulation for simulation who finised",xlab="birth rate ",main="pop at end without extinctions")
abline(h=nrow(smallpop),col="red")

allfinal=sapply(allpopsiz,function(i)i[length(i)])
boxplot(allfinal~bs,ylab="population size at the end of simulation for simulation who finised",xlab="birth rate ",main="pop at end ")
abline(h=nrow(population),col="red")

plot(allpopsiz[[1]],xlim=c(0,500),ylim=c(0,800))
compressedts=sapply(1:500,function(t)sapply(allpopsiz,function(i)i[t]))
getdist=apply(compressedts,2,quantile)

compressedts=sapply(1:500,function(t)sapply(allpopsiz,function(i)i[t]))

uniqutest=modelVector(K=K, m=1, b=b, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=500, tp=initNeutralTraitsPathways(z=2),age.threshold=20, out=c("popsize","births","deaths","repros","finalcomus","finalpop","popfull"),logging=c("done","time"),ma=1,traitsid=traitsid,F_Th=50,testdebug=F)

allpopu=sapply(uniqutest$popfull,function(population){
sapply(1:25,function(c){
           print(c)
           subpop=population[population[,"community"]==c,,drop=F]
           if(length(subpop)!=0){
               sum(validCouple(subpop,maturity=18,endrepro=65))
           }
           else
               NA
})
})
plot(1,1,type="n",ylim=c(0,1),xlim=c(0,500))
for(co in 1:25){
    lines(allpopu[co,],lwd=2,col=co)
}

allsize=sapply(uniqutest$popfull,function(population){
sapply(1:25,function(c){
           print(c)
           subpop=population[population[,"community"]==c,,drop=F]
           if(length(subpop)!=0){
           nrow(subpop)
           }
           else
               NA
})
})
simuresu=readRDS("fullout.RDS")

repros=apply(sapply(1:500,function(t)apply(simuresu,2,function(i)i$repros[t])),2,quantile,na.rm=T)
popsizes=apply(sapply(1:500,function(t)apply(simuresu,2,function(i)i$popsize[t])),2,quantile,na.rm=T)
popsizes=apply(sapply(1:500,function(t)apply(simuresu,2,function(i)i$popsize[t])),2,quantile,na.rm=T)

allpopsiz=sapply(1:500,function(t)apply(simuresu,2,function(i)i$popsize[t]))
allrepros=sapply(1:500,function(t)apply(simuresu,2,function(i)i$repros[t]))
alldeaths=sapply(1:500,function(t)apply(simuresu,2,function(i)i$deaths[t]))
allbirths=sapply(1:500,function(t)apply(simuresu,2,function(i)i$births[t]))
deaths=apply(alldeaths,2,quantile,na.rm=T)
births=apply(allbirths,2,quantile,na.rm=T)
plot(allpopsiz,allrepros)
hist(allrepros/allpopsiz)
plot(popsizes[1,],deaths[1,])
points(popsizes[1,],deaths[1,])
abline(0,0.04,col="red")
plot(popsizes[3,],births[3,])
abline(0,0.04,col="red")
text(450,15,expression(y==0.04*x),col="red") 
library(parallel)
cl<-makeCluster(10,type="FORK",outfile="log.txt")
allpopsiz=parSapply(cl,bs,function(b){
           res=modelVector(K=K, m=1, b=b, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=smallpop, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("popsize"),logging=c("done"),ma=1,traitsid=paste0("t",1:z),F_Th=180)
           res$popsize[length(res$popsize)]
})
stopCluster(cl)
